Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-09-19 cover-letter/resubmit-letter.tex
Fix minor typos

To aid in reviewing this new manuscript, I am including here a detailed summary of the changes in this new submission.
\begin{itemize}
  \item We revised the introduction to make clear the problem being solved relative to existing work and state the novelty of our contribution. It has also been expanded to address upfront the other requests, highlighted by the editor, in the prior review to (1) describe the dependency on the chosen language and tools; (2) define the limitations of the approach, and (3) discuss how this approach could be extended to other domains.
  \item We added a new section summarizing BriefCASE, with its many tools, and its general workflow. That section additionally makes clear the parts of BriefCASE that relate to our contributions in the paper.
  \item We added a new workflow diagram to the section discussing the illustrative example to show the inputs, outputs, existing adopted tools, and new tools that are part of the contribution of this work. We also removed from the example anything in BriefCASE that is not directly related to the contributions discussed in this submission.
  \item We have grouped into a section titled "Background" everything relating to the AGREE tool as it is an existing tool that we leverage as part of our solution to the synthesis problem.
  \item We have revised the case study to identify roles in identifying and adding requirements.
  \item We have completely revised the related work to contrast our solution to synthesis relative to the existing solutions with an effort to highlight that we have solved the problems identified in the introduction. We have also added new related work as suggested by the reviewers and other related work that we have became aware of since submitting our original paper.
  \item We have revised the conclusion to be specific in the planned and ongoing future work as requested by the reviewers. In particular, we have detailed how we plan to fully verify the transformation from a code contract to CakeML and reported on some early results in that regard. We have also referenced ongoing useability studies with Collins designers.
  \item We have made several edits through the document for consistency and to address other specific reviewer comments.
\end{itemize}

>>>>

To aid in reviewing this new manuscript, I am including here a detailed summary of the changes in this new submission.
\begin{itemize}
  \item We revised the introduction to make clear the problem being solved relative to existing work and state the novelty of our contribution. It has also been expanded to address upfront the other requests, highlighted by the editor, in the prior review to (1) describe the dependency on the chosen language and tools; (2) define the limitations of the approach, and (3) discuss how this approach could be extended to other domains.
  \item We added a new section summarizing BriefCASE, with its many tools, and its general workflow. That section additionally makes clear the parts of BriefCASE that relate to our contributions in the paper.
  \item We added a new workflow diagram to the section discussing the illustrative example to show the inputs, outputs, existing adopted tools, and new tools that are part of the contribution of this work. We also removed from the example anything in BriefCASE that is not directly related to the contributions discussed in this submission.
  \item We have grouped into a section titled "Background" everything relating to the AGREE tool as it is an existing tool that we leverage as part of our solution to the synthesis problem.
  \item We have revised the case study to identify roles in identifying and adding requirements.
  \item We have completely revised the related work to contrast our solution to synthesis relative to the existing solutions with an effort to highlight that we have solved the problems identified in the introduction. We have also added new related work as suggested by the reviewers and other related work that we have become aware of since submitting our original paper.
  \item We have revised the conclusion to be specific in the planned and ongoing future work as requested by the reviewers. In particular, we have detailed how we plan to fully verify the transformation from a code contract to CakeML and reported on some early results in that regard. We have also referenced ongoing useability studies with Collins designers.
  \item We have made several edits through the document for consistency and to address other specific reviewer comments.
\end{itemize}

### 2022-09-19 paper/intro.tex
Add CASE in footnote
Fix minor typos

In recent years, aerospace stakeholders have realized that avionics
systems are subject to possible cyber-attacks just like other
cyber-physical systems.
%
\footnote{This work was funded in part by the
Defense Advanced Research Projects Agency (DARPA).  The views
expressed are those of the authors and do not reflect the official
policy or position of DARPA or the U.S. Government.}
%
Thus, in addition to being fault-tolerant, safety-critical avionics
systems must also be {\em cyber-resilient}.  Cyber-resiliency means
that the system is tolerant to cyber-attacks just as safety-critical
systems are tolerant to random faults: they recover and continue to
execute their mission function, or safely shut down, as requirements
dictate.

@@

{\brfcs} is open source and publicly available \cite{fmide}, as are the
examples and case study we discussed in this paper \cite{repo,
phase2, camkes, case}.

@@

As indicated in the preceding discussion, {\brfcs} is aimed at
addressing the lack of tool support for the the problem of enforcing
and implementing the class of \emph{cyber-resilience} system
requirements.  Our approach to the problem is embedded in a
substantial collection of tools, so it is important to clarify the
research impact. We see the following as the distinguishing
contributions of this paper:

@@

Our approach currently applies to common cyber-vulnerabilities, such
as buffer overflow, lack of input validation, and supply-chain issues;
however, other cyber-vulnerabilities such as side-channel attacks and
denial of service have not yet been addressed. Moreover, this work
does not introduce a new type of high-assurance component in terms of
capability. Instead, our contribution is in the automated synthesis of
security-improving components from formal cyber-resilience
specifications, paired with a verification showing that the
synthesized implementation is correct. We have not yet tried to apply
{\brfcs} to problems outside the realm of cyber-resilience; however,
the notions of code and test contracts, along with the system analysis
and verified code generation facilities promise to be useful in a wide
variety of settings.

>>>>

In recent years, aerospace stakeholders have realized that avionics
systems are subject to possible cyber-attacks just like other
cyber-physical systems.
%
\footnote{This work was funded in part by the
Defense Advanced Research Projects Agency (DARPA) CASE program.  The views
expressed are those of the authors and do not reflect the official
policy or position of DARPA or the U.S. Government.}
%
Thus, in addition to being fault-tolerant, safety-critical avionics
systems must also be {\em cyber-resilient}.  Cyber-resiliency means
that the system is tolerant to cyber-attacks just as safety-critical
systems are tolerant to random faults: they recover and continue to
execute their mission function, or safely shut down, as requirements
dictate.

@@

{\brfcs} is open source and publicly available \cite{fmide}, as are the
examples and case study we discuss in this paper \cite{repo,
phase2, camkes, case}.

@@

As indicated in the preceding discussion, {\brfcs} is aimed at
addressing the lack of tool support for the problem of enforcing
and implementing the class of \emph{cyber-resilience} system
requirements.  Our approach to the problem is embedded in a
substantial collection of tools to be wholistic in addressing cyber-resilience at the system level, so it is important to clarify the
research impact. We see the following as the distinguishing
contributions of this paper:

@@

Our approach currently applies to common cyber-vulnerabilities, such
as buffer overflow, lack of input validation, and supply-chain issues;
however, other cyber-vulnerabilities such as side-channel attacks and
denial of service have not yet been addressed. Moreover, this work
does not introduce a new type of high-assurance component in terms of
capability. Instead, our contribution is in the automated synthesis of
security-improving components from formal cyber-resilience
specifications, paired with a verification showing that the
synthesized implementation is correct in the context of the whole system all the way down to the binary implementation.

We have not yet tried to apply
{\brfcs} to problems outside the realm of cyber-resilience; however,
the notions of code and test contracts, along with the system analysis
and verified code generation facilities promise to be useful in a wide
variety of settings. Writing code and test contracts does require a working knowledge of propositional logic but not to a degree that would exceed what would be expected in a designer. The general synthesis approach in this paper could be used outside of the \brfcs\ environment, but it would only then provide guarantees relative to the complied artifacts and not say anything about the correctness of the system composition.
